# 贝叶斯与 MCMC {#bayes}

```{r setup, include = FALSE}
source("common.R")
```

## 贝叶斯计算

### MCMC

最大后验估计，贝叶斯分层模型


### Stan

从 WinBUGS\index{WinBUGS} 到 OpenBUGS\index{OpenBUGS}，从 JAGS\index{JAGS} 到 Stan\index{Stan}，BUGS\index{BUGS}的发展从未停止过，Stan^[<http://mc-stan.org/>] 是一个统计建模和高性能统计计算平台。

Stan 提供的R语言接口 rstan 包 [@R-rstan] 及其扩展 StanHeaders 包 [@R-StanHeaders] 、bayesplot包 [@R-bayesplot] 、brms 包 [@brms2017JSS]、 rstanarm 包 [@R-rstanarm] 以及 rstan 的 wiki^[<https://github.com/stan-dev/rstan/wiki>] 及其在空间广义线性混合效应模型的参数估计和预测中的应用。


安装 rstan

```{r install-rstan, eval = (!"rstan" %in% .packages(TRUE))}
install.packages("rstan", dependencies = TRUE)
```

加载 rstan,如果你的电脑配置有多核处理器，内存也充足，那么可以考虑使用并行方式去估计你的模型参数，

```{r setup-rstan, eval = ("rstan" %in% .packages(TRUE))}
library(rstan)
rstan_options(auto_write = TRUE)
options(mc.cores = parallel::detectCores())
```

安装 brms

```{r, eval = ("brms" %in% .packages(TRUE))}
install.packages("brms", dependencies = TRUE)
```


1. Bayesian Data Analysis <https://github.com/avehtari/BDA_R_demos>
Bayesian Data Analysis, 3rd ed by Gelman, Carlin, Stern, Dunson, Vehtari, and Rubin (BDA3).

2. RStan Book <https://github.com/MatsuuraKentaro/RStanBook> 这是日文版

3. An Introduction to State Space Time Series Analysis <https://github.com/sinhrks/stan-statespace>
Stan models for state space time series

4. Draft introduction to probability and inference aimed at the Stan manual. <https://github.com/betanalpha/stan_intro>


5. Bayesian Modeling using Stan
<https://github.com/fonnesbeck/stan_workshop_2016>
Bayesian Modeling using Stan in R (May/June 2016)

6. Define Stan models using glmer-style (lme4) formulas
<https://github.com/rmcelreath/glmer2stan>

7. Examples of working and non-working models, initially for ODCS 2016 in Boston.
<https://github.com/sakrejda/stan-workshop>

8. State space models (dynamic linear models, hidden Markov models) implemented in Stan
<https://github.com/jrnold/ssmodels-in-stan>

9. State Space Models in Stan <https://jrnold.github.io/ssmodels-in-stan/>

10. Conditional autoregressive models in Stan <https://github.com/mbjoseph/CARstan>

11. Implementation of B-Splines in Stan <https://github.com/milkha/Splines_in_Stan>

12. <https://magesblog.com/post/correlated-lognormal-chain-ladder-model/>

