--- 
title: "The R Box"
subtitle: "Notes on R, Octave, Python, Graphics, Models and Others"
author: "Xiangyun Huang"
date: "`r format(Sys.time(), tz = 'Asia/Taipei', usetz = TRUE)`"
site: bookdown::bookdown_site
geometry: margin=1.18in
documentclass: ctexbook
bibliography: [book.bib, packages.bib]
biblio-style: apalike
lof: yes
lot: yes
graphics: yes
tables: yes
link-citations: yes
links-as-notes: no
colorlinks: yes
toccolor: magenta
classoption: "a4paper, table, x11names"
description: "This is a minimal example of using the bookdown package to write a book. The output format for this example is bookdown::gitbook."
---

# 序言 {#foreword}

```{r fig.align='center', eval=knitr::is_html_output(), echo=FALSE, include=identical(knitr:::pandoc_to(), 'html'), fig.link='https://www.r-project.org/logo/', out.width='25%'}
knitr::include_graphics('images/Rlogo.svg')
```

自序是由作者说明著作意图、写书经过、内容体例等情况；他序是由权威人士评价、推荐著作和作者以及对书稿有关问题的研究阐述。This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.name/tinytex/>.

```{r include=FALSE,cache=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown', 'tinytex'
), 'packages.bib')
```
