--- 
title: "A Minimal Book Example"
author: "黄湘云"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
geometry: margin=1.18in
documentclass: ctexbook
bibliography: [book.bib, packages.bib]
biblio-style: apalike
lof: yes
lot: yes
graphics: yes
tables: yes
link-citations: yes
colorlinks: yes
classoption: "hyperref, a4paper, UTF8, zihao = -4, linespread = 1.3"
description: "This is a minimal example of using the bookdown package to write a book. The output format for this example is bookdown::gitbook."
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  echo = TRUE,
  # cache = TRUE,
  out.width = "70%",
  fig.align = 'center',
  fig.width = 6,
  fig.asp = 0.618,  # 1 / phi
  fig.show = "hold"
)
```

\mainmatter

# 前言 {#preface}

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.name/tinytex/>.

Pandoc\index{Pandoc} and Hugo\index{Hugo}

## 设置字体

安装 showtext 包[@Qiu2015]和思源字体

```{r font-setup, eval= (!"showtext" %in% .packages(TRUE))}
install.packages("showtext",dependencies = TRUE)
library(showtext)
# Install Source Han Sans/Serif font (by default Simplified Chinese)
font_install(source_han_serif("CN")) # 思源宋体
font_install(source_han_sans("CN"))  # 思源黑体
```

showtext 包可以调用系统字体，图\@ref(fig:demo-ggplot2)使用5号思源宋体，英文和数字使用 serif 字体。详细的使用文档可以看 [showtext 的开发页面](https://github.com/yixuan/showtext)

```{r demo-ggplot2, fig.showtext = TRUE,fig.cap="showtext包处理图里的中文"}
library(ggplot2)
ggplot(iris, aes(Sepal.Length, Sepal.Width)) +
  geom_point(aes(colour = Species)) +
  scale_colour_brewer(palette = "Set1") +
  labs(
    title = "鸢尾花数据的散点图",
    x = "萼片长度", y = "萼片宽度", colour = "鸢尾花类别"
  ) +
  theme_minimal(base_size = 10.54, base_family = "source-han-serif-cn") +
  theme(
    legend.text = element_text(family = "serif", size = 10.54),
    axis.text = element_text(family = "serif", size = 10.54)
    )
```

这篇文章主要使用 ggplot2 包[@Wickham2016]绘图，为了好玩我们还使用 xkcd 字体，先下载和加载 xkcd 包[@R-xkcd]

```{r xkcd-setup, eval=(!"xkcd" %in% .packages(TRUE))}
install.packages("xkcd",dependencies = TRUE)
library(xkcd)
```

下载和注册 xkcd 字体

```{r download-xkcd, eval= (!'xkcd' %in% extrafont::fonts())}
download.file("http://simonsoftware.se/other/xkcd.ttf",
  dest = "xkcd.ttf", mode = "wb"
)
system("mkdir ~/.fonts")
system("cp xkcd.ttf ~/.fonts")
library(extrafont)
font_import(pattern = "[X/x]kcd", prompt = FALSE)
if (.Platform$OS.type != "unix") {
  ## Register fonts for Windows bitmap output
  loadfonts(device = "win")
} else {
  loadfonts() # 注册字体
}
fonts() # 查看可用的字体
```

图 \@ref(fig:xkcd-demo) 是一个简单的使用例子

```{r xkcd-demo,fig.cap="xkcd 风的图"}
p <- ggplot() + geom_point(aes(mpg, wt), data = mtcars) +
  theme_xkcd()
p
```

安装 fontcm 包[@R-fontcm]处理数学公式，下载 fontcm 包^[<https://github.com/wch/fontcm>] 和相关字体

```{r download-fontcm, eval=(!"fontcm" %in% .packages(TRUE))}
library(extrafont)
font_install('fontcm')
loadfonts() # 注册字体
```

一个小demo如下

```{r fontcm-demo,eval=FALSE}
library(fontcm)
pdf("figures/ggplot_cm.pdf", width = 4, height = 4)
p <- qplot(c(1, 5), c(1, 5)) +
  xlab("Made with CM fonts") + ylab("Made with CM fonts") +
  ggtitle("Made with CM fonts")

# Equation
eq <- "italic(sum(frac(1, n*'!'), n==0, infinity) ==
       lim(bgroup('(', 1 + frac(1, n), ')')^n, n %->% infinity))"

# Without the new fonts
p + annotate("text", x = 3, y = 3, parse = TRUE, label = eq) # fig 1

# With the new fonts
p + annotate("text",
  x = 3, y = 3, parse = TRUE,
  family = "CM Roman", label = eq
) +
  theme(
    text = element_text(size = 16, family = "CM Roman"),
    axis.title.x = element_text(face = "italic"),
    axis.title.y = element_text(face = "bold")
  ) # fig 2
dev.off()
# 使用 ghostscript 嵌入数学字体
# Embed the fonts
embed_fonts("figures/ggplot_cm.pdf", outfile = "figures/ggplot_cm_embed.pdf")
```

使用 fontcm 包，效果如图\@ref(fig:fontcm-ggplot)所示

```{r fontcm-ggplot, echo=FALSE,fig.cap="fontcm 处理数学公式"}
knitr::include_graphics("figures/ggplot_cm_embed.pdf")
```


## 软件信息

系统安装的 R 包有：

```{r}
.packages(TRUE)
```


R 软件运行环境：

```{r}
devtools::session_info()
```


```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown','showtext',
  'ggplot2','rstan','xkcd'
), 'packages.bib')
```
