---
title: "Untitled"
output: 
  github_document:
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  engine.path = list(
#    octave = "/usr/bin/octave-cli",
    python = "D:/Anaconda3/python.exe"
  )
  )
```

This is a minimal example of a book based on R Markdown and **bookdown** (https://github.com/rstudio/bookdown). Please see the page "Get Started" at https://bookdown.org/ for how to compile this example.

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

```{python}
print('hello')
```


```{python, dev = "png", eval = T}
import numpy as np
import matplotlib.pyplot as plt
plt.switch_backend('agg') # Very Important in R Markdown

# Example data
t = np.arange(0.0, 1.0 + 0.01, 0.01)
s = np.cos(4 * np.pi * t) + 2

plt.rc('text', usetex=True)
plt.rc('font', family='serif')
plt.plot(t, s)

plt.xlabel(r'\textbf{time} (s)')
plt.ylabel(r'\textit{voltage} (mV)',fontsize=16)
plt.title(r"\TeX\ is Number "
          r"$\displaystyle\sum_{n=1}^\infty\frac{-e^{i\pi}}{2^n}$!",
          fontsize=16, color='gray')
# Make room for the ridiculously large title.
plt.subplots_adjust(top=0.8)

# plt.savefig('tex_demo')
plt.show()
```

